---
title: "Barcode lookup for WGS choices"
output: html_notebook
---

```{r}
library(here)
library(ggplot2)
```

This notebook details how we used Sanger reads of BCs from individual 2N clones to decide on which cloces to perform WGS for the following environments:

1. SC 37C
2. SC pH7.3
3. 0.2M NaCl
4. SC 21C

First we load the barcodes extracted form the Sanger reads:
```{r}
#set_here(path = "/Users/phumph/Dropbox/PLT/sequencing_info/dBFA2_BC_checks_for_WGS/parsed_BCs_and_wells_mapped/")
plates <- Sys.glob(here("data/dBFA2_parsed_BCs_and_wells_mapped/*.csv"))

# laod fitness file
fitnesses <- read.csv(here('data/dBFA2_fitnesses_with_adapt_20APR2018.csv'))
```

Run through each `plates` entry and add adapted column (0, 1, or NA) along with fitness estimate, also parsing well_ID based on Sanger plate ID built into the name. There are two naming conventions, and each requires its own, so perhaps I'll have to do this manually.

Define functions:
```{r}
str_splitter <- function(x, sp, nm){
  x2 <- unlist(strsplit(x, sp))[nm]
}

# well-mapper
# assumes column-wise numbering
well_mapper <- function(x){
  the_map <- c('A' = 1,
                  'B' = 2,
                  'C' = 3,
                  'D' = 4,
                  'E' = 5,
                  'F' = 6,
                  'G' = 7,
                  'H' = 0)
  mod8 <- x %% 8
  the_row <- names(the_map)[match(mod8,the_map)]
  the_col <- ceiling(x/8)
  if(the_col<10){
    the_col <- paste0('0',the_col)
  }
  the_id <- paste0(the_row,the_col)
  return(the_id)
}
```



```{r}
files <- list()
for (file in 1:length(plates)){
  files[[file]] <- read.csv(plates[file])
}

split_on <- data.frame(t(matrix(c('_',3,'_',6,'_',2,'_',2),nrow= 2)))
split_on$X2 <- as.numeric(as.vector(split_on$X2))
the.res <- list()
for (f in 1:length(files)){
  # define new working file
  the.file <- data.frame(files[f])
  
  # initialize Full.BC column
  the.file$Full.BC <- '0'
  
  # rename columns
  names(the.file) <- c('ID','Diverse.BC','Environment.BC', 'Full.BC')
  
  # parse names:
  the.file$Full.BC <- paste0(the.file$Diverse.BC,the.file$Environment.BC)
  
  # merge with fitness file
  the.file2 <- merge(the.file, fitnesses, by = 'Full.BC', sort = F)
  #length(unique(the.file2$Full.BC[the.file2$adapted==1]))
  
  # now, parse IDs to find wells:
  # split on indicated character, indexed by 'file':
  the.file2$id_well <- sapply(paste0(the.file2$ID), str_splitter, sp = paste0(split_on[f,1]), nm = split_on[f,2])
  the.file2$id_well <- gsub('.ab1','',the.file2$id_well)
  the.file2$id_well <- gsub('-PLR2','',the.file2$id_well)
  
  # now, output this:
  the.res[[f]] <- dplyr::arrange(the.file2, id_well)
}

```

Now, generate output for printing:

```{r}
# pass the right source env. to script:
target_cols <- c('Full.BC','sources','subpool','ID','id_well','adapted')
#paste0(here("data/dBFA2_parsed_BCs_and_wells_mapped/"),plates[f])

output_adapteds <- function(x, target_cols = target_cols, fname){
  df.tmp <- x[,names(x) %in% target_cols]
  df.tmp <- df.tmp[df.tmp$adapted == 1,]
  df.tmp2 <- dplyr::group_by(df.tmp, Full.BC) %>% dplyr::summarise(ID=unique(ID)[1], sources = unique(sources)[1], subpool = unique(subpool)[1], n_wells = length(id_well), first_well = unique(id_well)[1]) %>% dplyr::arrange(first_well)
  #df.tmp3 <- merge(df.tmp, data.frame(df.tmp2), all.x = F, all.y = F, by = 'Full.BC', sort = F)
  write.csv(df.tmp2, file = fname,quote = F, row.names = F)
}

for (f in 1:length(files)){
  output_adapteds(the.res[[f]], target_cols = target_cols, fname = paste0(gsub('.csv','',plates[f]),'_parsed.csv'))
}
```
