---
title: "More BC Reconciling"
output: html_notebook
---


Steps:

1. Pull in `Subpool.Environment` from BFA data
2. Hit each called barcode against it, focusing on the conflicting calls.
3. Determine whether we have enough evidence to support one call over the other.
4. Parse sub-calls and look at intersection of each set called for each WGS sample.

Let's bring in the BFA data to capture `Subpool.Environment` BC sets:
```{r}
bfa.dat <- read.csv("data/dBFA2_hBFA1_fitnesses_allBCs.csv")
bfa.dat <- read.csv("data/dBFA2_counts_with_env_info.csv")
head(bfa.dat)
```

Now load up WGS barcodes with conflicts:
```{r}
bcs <- read.csv("data/mutations/final_BC_calls_2019-MAY-21/bcs_transformed_2019-JUN-18.csv")
head(bcs)
```

Hit each barcode against the fitness data to figure out subpool information:
```{r}
bfa.dat2 <- bfa.dat[,c('Full.BC','Diverse.BC','Environment.BC','Total.Counts',grep('Subpool', names(bfa.dat), value = T))]

x <- bcs$LH_Diverse.BC[5]
y <- bfa.dat2
input_col <- 'LH_Diverse.BC'
target_col = 'Diverse.BC'

bc_compare <- function(x, y, input_col = NULL, target_col = NULL){
  # for each input x, hit diverse BC call against set of input reference BCs in y
  hit <- y[grep(paste0(x), y[,target_col]),]
  
  if (dim(hit)[1]>0){
    y2 <- data.frame(x,hit)
    names(y2)[1] <- input_col
  } else {
    y2 <- data.frame(x, Full.BC = NA,
                     Diverse.BC = NA,
                     Environment.BC = NA, 
                     Total.Counts = NA,
                     Subpool.Environment = NA,
                     Which.Subpools = NA)
    names(y2)[1] <- input_col
  } 
  return(y2)
}

bcs_1 <- sapply(bcs$LH_Diverse.BC, function(x) bc_compare(paste0(x), y = bfa.dat2, input_col = 'LH_Diverse.BC', target_col = 'Diverse.BC'))


debug(sapply(bcs$LH_Diverse.BC, function(x) bc_compare(paste0(x), y = bfa.dat2, input_col = 'LH_Diverse.BC', target_col = 'Diverse.BC'))
)

# do as loop to find where it breaks:
  input_col <- 'LH_Diverse.BC'
  target_col = 'Diverse.BC'
  hits <- data.frame(NA)
  
for (b in 1:length(bcs[,1])){
  hits[b,] <- bc_compare(paste0(bcs[b,input_col]), y = bfa.dat2, input_col = 'LH_Diverse.BC', target_col = 'Diverse.BC')
}

  
# don't bother with any of this; just join
  
bcs2 <- dplyr::left_join(bcs, bfa.dat2, by = c('LH_Diverse.BC' = 'Diverse.BC'))
bcs3 <- dplyr::left_join(bcs2, bfa.dat2, by = c('YL_Diverse.BC' = 'Diverse.BC'))

table(bcs2$Subpool.Environment, bcs2$SOURCE)
table(bcs3$Subpool.Environment, bcs3$SOURCE)

table(bcs3$Subpool.Environment.x, bcs3$Subpool.Environment.y)

# now plot for only those discrepant ones:
with(bcs3[bcs3$DBC_conflict==TRUE,], table(Subpool.Environment.x, Subpool.Environment.y))
```

OK so there is no discrepancy between calls as to which subpool environment they came from. I now need to do the reciprocal grep to see whether they're at least seeing the same barcodes.

